Lattice model

### 2017-04-03 oopsla17/lattice-model.tex
Add base case to Exact Set
Elaborate how subset and superset relations are computed

Here is the mathematical definition of consistency checking:
\begin{align*}
  \textit{consistent}(\textit{ix}, \textit{model}) & = \begin{cases}
    \mathsf{false} & \textit{model} = \mathsf{once}(x) \wedge ix = \mathsf{mult}(y) \\
    \textit{consistent'}(\textit{peel}(ix), \textit{peel}(model)) & \textit{otherwise}
  \end{cases} \\
%
  \textit{consistent'}(\textit{ix}, \textit{model}) & = \begin{cases}
    m = ix & \textit{model} = \mathsf{exact}(m) \\
    m \supseteq ix & \textit{model} = \mathsf{upper}(m) \\
    m \subseteq ix & \textit{model} = \mathsf{lower}(m)
  \end{cases}
\end{align*}

Here helper function $\textit{peel} : \mathsf{Approx} \; a \to a$ removes the
approximation label.

\todo{Here we simply show \textit{consistency'} as set equality/subset/superset,
but since sets are infinite we might need to elaborate based on representation.}

@@

\todo{On the following, add some intutition first- what is this and
  what is it for?}
\begin{defn}{(Exact set)}
  The \emph{exact set} at origin distance $d$, $\mathit{ES}_{P,d}$, of a group
  of $N$ dimensional points $P$ is defined below:
%
  \begin{equation*}
    \mathit{ES}_{P,d} =
      \{ p \in P \mid \forall i.\
         p_i \notin \{-1,0,1\} \implies
         \exists p' \in \mathit{ES}_{P,d-1}.\ p' =
         \mathit{close\_neighbour}(p,i) \}
  \end{equation*}
%
  The overall \emph{exact set}, $\mathit{ES}_P$ is then
  $\bigcup_{1 \leq d \leq D} \mathit{ES}_{P,d}$, where $D$ is the maximum origin
  distance in $P$.
\end{defn}
\todo{Ah, I think I am starting to understand, but at 
$\mathit{ES}_{P,1}$ then we end up saying there exists a 
$p'$ in $\textit{ES}_{P,0}$, but we don't calculate that set...
so how does this end?}

>>>>

Here is the mathematical definition of consistency checking:
\begin{align*}
  \mathit{consistent}(\mathit{ix}, \mathit{model}) & = \begin{cases}
    \mathsf{false} & \mathit{model} = \mathsf{once}(x) \wedge ix = \mathsf{mult}(y) \\
    \mathit{consistent'}(\mathit{peel}(ix), \mathit{peel}(model)) & \textit{otherwise}
  \end{cases} \\
%
  \mathit{consistent'}(\mathit{ix}, \mathit{model}) & = \begin{cases}
    m = \mathit{ix} & \mathit{model} = \mathsf{exact}(m) \\
    m \supseteq \mathit{ix} & \mathit{model} = \mathsf{upper}(m) \\
    m \subseteq \mathit{ix} & \mathit{model} = \mathsf{lower}(m)
  \end{cases}
\end{align*}

Here helper function $\mathit{peel} : \mathsf{Approx} \; a \to a$ removes the
approximation label.

Due to use of infinite intervals, the model and index sets are potentially
infinite meaning simple procedures used to compute equality, subset, and
superset relations for finite sets are no avail. The subset and superset
relations are handled by computing the intersection of $m$ and $\mathit{ix}$
using \Cref{lem:vector-intersect}, then checking equality with $m$ and
$\mathit{ix}$ respectively.

\todo{Here we simply show \textit{consistency'} as set equality, but since sets
are infinite we might need to elaborate based on representation.}

@@

\todo{On the following, add some intutition first- what is this and
  what is it for?}
\begin{defn}{(Exact set)}
  The \emph{exact set} at origin distance $d$, $\mathit{ES}_{P,d}$, of a group
  of $N$ dimensional points $P$ is defined below:
%
  \begin{align*}
    \mathit{ES}_{P,0} & = \{ p \in P \mid \forall \i.\ \pi_i(p) \in \interv{-1}{1}{} \} \\
    \mathit{ES}_{P,d} & =
      \{ p \in P \mid \forall i.\
      p_i \notin [-1,1] \implies
         \exists p' \in \mathit{ES}_{P,d-1}.\ p' =
         \mathit{close\_neighbour}(p,i) \}
  \end{align*}
%
  The overall \emph{exact set}, $\mathit{ES}_P$ is then
  $\bigcup_{1 \leq d \leq D} \mathit{ES}_{P,d}$, where $D$ is the maximum origin
  distance in $P$.
\end{defn}
